---
title: "Minimal example of UC Berkeley Beamer Theme"
author: "Zachary Lorico Hertz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  beamer_presentation:
    latex_engine: "xelatex"
    includes:
      in_header:
        - beamerthemeUCBerkeley.sty
urlcolor: BerkeleyGold
bibliography: example.bib
suppress-bibliography: true
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(gridExtra)
library(modelsummary)
le_dat <- read.csv("ledb_candidatelevel.csv")
```

```{r, include=FALSE}
model <- lm(vote_share ~ incumbent + pid_est, data=le_dat)
```

# This is a quick and dirty Beamer Template
- Beamer is often used by academics to virtue-signal their ability to use LaTeX
- I like using Beamer in an .rmd file in this case because it makes it easy to produce slides in a working directory nested in my project folder
- This lets me tweak figures in my slides using the R code, or read plots in from R code elsewhere in the directory, in a simple way.
- Sometimes you need to do nested bullet points.
    + You do this in a particular manner:
        + Add a plus sign
        + Then tab and voila. 

# Using LaTeX in your slides

Sometimes you need to use LaTeX in slides (e.g. to present your model). For example:

\begin{align*}
\text{Vote Share}_{i} = \beta_0 &+ \beta_1 \times \text{Incumbent}_{i} + \epsilon_{i}
\end{align*}

# Sometimes, to make your point...

>- It becomes necessary to progress through bullets one at a time.
>- To do this, just add a $>$ to the front of your bullet points.
>   + This also works with sub bullets!
>   + As so.

# This is also powerful because
- It works with citations and can read those in with your usual .bib keys.
- This point is made by previous citations [@hertz2023].
- Note that in its current form, I am suppressing the Works Cited at the end. You can modify this by changing `suppress-bibliography: true` in the YAML.

# Presenting regression results
```{r, echo=FALSE}
modelsummary(model,
             stars = c('*' = .05, '**' = .01, '***' = 0.001),
             title= "Example Regression Model",
             gof_map = c("nobs", "r.squared", "rmse", "F"),
             coef_rename = c("incumbent" = "Incumbency",
                             "pid_estR" = "Republican"),
             output="markdown")
```


# Results: Plotting in Beamer
```{r, echo=FALSE, warning=FALSE}
le_dat %>% 
  filter(!is.na(incumbent)) %>% 
  ggplot(aes(x=vote_share, color=as.factor(incumbent))) +
  geom_density() +
  theme_minimal()
```

# Thank you!

\begin{center}
Zachary Lorico Hertz
\linebreak
\href{https://twitter.com/zacharylhertz}{$@$zacharylhertz} 
\linebreak
\href{mailto:zachary_hertz@berkeley.edu}{zachary\_hertz$@$berkeley.edu} 
\end{center}
